cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Completed trigonometric_tb

```{r}
#| label: import-scripts
source("scripts/additional_functions.R")
```
# Introduction

@@

@@

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("",
                                "",
                                "",
                                "",
                                "",
                                ""))
```

>>>>

```{r}
#| label: import-scripts
source("scripts/additional_functions.R")
```

# Introduction

@@

```{r data-expbranches}
expbranches <- gen_expbranches(n = 1000, p = 4, k = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(expbranches)
```

@@

```{r data-bluntedcone}
bluntedcone <- gen_bluntedcone(n = 1000, p = 4, h = 5, ratio = 0.5)
```

```{r, eval=FALSE}
langevitour::langevitour(bluntedcone)
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("Generate a crescent pattern.",
                                "Generate a curvy cylinder.",
                                "Generate a spherical spiral.",
                                "Generate a helical spiral.",
                                "Generate a conic spiral.",
                                "Generate a nonlinear hyperbola."))
```
